Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-28 text/src/article.tex
Outline for scaffolder discussion section

>>>>

Pros
  * Reproducable steps in building a scaffold
  * Extensive documentation. Should be easy to use as possible.
  * Scaffold file allows meaningful construction of a scaffold
  * See of each sequence in building final draft genome
  * Keeping genome sequence in a scaffold file means it is simpler to edit after the fact.
  * Versionable plain text. Easy to store and see diffs
  * Common format for scaffold file means it can be easily manipulated programmatically.
  * Command line interface for using as is
  * Ruby API allowing more complex manipulation of the scaffold
  * Simple to install.  Automatically installed. No manual installation.
